The Role of Variability in Learning Generalization: A Computational Modeling Approach

### 2024-10-20 Manuscript/manuscript.qmd
re-render after fixing ugs revision issues
fix issue with figure 28 overlapping with page number

::: {.content-visible when-format="docx"}
{{< include pre_sections/pre_docx.qmd >}}
{{< include pre_sections/acknowledgements.qmd >}}
{{< include pre_sections/abstract.qmd >}}
:::

@@

```{r}
#| label: fig-htw-resid-pred
#| fig-cap: "Model residuals for each combination of training condition, fit method, and model. Residuals reflect the difference between observed and predicted values. Lower values indicate better model fit. Note that y-axes are scaled differently between facets. A) Residuals predicting each block of the training data. B) Residuals predicting each band during the testing stage. Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands."
#| fig-height: 14
#| fig-width: 11

>>>>

::: {.content-visible when-format="docx"}
{{< include pre_sections/pre_docx.qmd >}}
:::

@@

```{r}
#| label: fig-htw-resid-pred
#| fig-cap: "Model residuals for each combination of training condition, fit method, and model. Residuals reflect the difference between observed and predicted values. Lower values indicate better model fit. Note that y-axes are scaled differently between facets. A) Residuals predicting each block of the training data. B) Residuals predicting each band during the testing stage. Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands."
#| fig-height: 13.5
#| fig-width: 11

### 2024-10-20 Sections/full.qmd
fix issue with figure 28 overlapping with page number

::: {.content-visible unless-format="markdown"}
```{dot}
//| label: fig-design-e2
//| fig-cap: "Experiment 2 Design. Constant and Varied participants complete different training conditions. The training and testing bands are the reverse of Experiment 1. "
//| fig-width: 7.0
//| fig-height: 2.2
//| fig-responsive: false
//| echo: false 
//| 
/////| column: screen-inset-right
digraph {
  graph [layout = dot, rankdir = LR]
  node [shape = rectangle, style = filled]
  data1 [label = " Varied Training \n100-300\n350-550\n600-800", fillcolor = "#00A08A"]
  data2 [label = " Constant Training \n600-800", fillcolor = "#FF0000"]
  Test3 [label = "    Final Test \n  Novel With Feedback  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
  data1 -> Test1
  data2 -> Test1
  subgraph cluster {
    label = "Test Phase \n(Counterbalanced Order)"
    Test1 [label = "Test  \nNovel Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
    Test2 [label = "  Test \n  Varied Training Bands  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
    Test1 -> Test2
  }
  Test2 -> Test3
}
```
:::

>>>>

::: {.content-visible unless-format="markdown"}
```{dot}
//| label: fig-design-e2
//| fig-cap: "Experiment 2 Design. Constant and Varied participants complete different training conditions. The training and testing bands are the reverse of Experiment 1. "
//| fig-width: 6.0
//| fig-height: 1.8
//| fig-responsive: false
//| echo: false 
//| 
/////| column: screen-inset-right
digraph {
  graph [layout = dot, rankdir = LR]
  node [shape = rectangle, style = filled]
  data1 [label = " Varied Training \n100-300\n350-550\n600-800", fillcolor = "#00A08A"]
  data2 [label = " Constant Training \n600-800", fillcolor = "#FF0000"]
  Test3 [label = "    Final Test \n  Novel With Feedback  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
  data1 -> Test1
  data2 -> Test1
  subgraph cluster {
    label = "Test Phase \n(Counterbalanced Order)"
    Test1 [label = "Test  \nNovel Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
    Test2 [label = "  Test \n  Varied Training Bands  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
    Test1 -> Test2
  }
  Test2 -> Test3
}
```
:::
